Evolving Robot Gaits in Hardware: the HyperNEAT Generative Encoding Vs. Parameter Optimization

### 2011-04-17 paper_ecal/platformDetails.tex
Changed URL to correct bit.ly link

All of the computation for gait learning, fitness evaluation, and
robot control was performed on the compact, on-board CompuLab Fit-PC2,
running Ubuntu Linux 10.10. 
The most computationally expensive portion of code was HyperNEAT, but even
this took less than one second to run on the on-board computer. Thus,
we chose not to offload any computation.
All gait generation, learning, and fitness
evaluation code, except HyperNEAT, was written in Python and is
available on our website (http://bit.ly/hLHBYq).  HyperNEAT is written in
C++.  We controlled the servos with the Pydynamixel library, sending commanded positions at 40Hz.  The robot
connected to a wireless network on boot, which enabled us to control
it via SSH.

>>>>

All of the computation for gait learning, fitness evaluation, and
robot control was performed on the compact, on-board CompuLab Fit-PC2,
running Ubuntu Linux 10.10. 
The most computationally expensive portion of code was HyperNEAT, but even
this took less than one second to run on the on-board computer. Thus,
we chose not to offload any computation.
All gait generation, learning, and fitness
evaluation code, except HyperNEAT, was written in Python and is
available on our website (http://bit.ly/ecalgait).  HyperNEAT is written in
C++.  We controlled the servos with the Pydynamixel library, sending commanded positions at 40Hz.  The robot
connected to a wireless network on boot, which enabled us to control
it via SSH.
